### 2010-10-14 papers/BMD2010/PhysicalParametersPaper/paper.tex
adding more stuff

%\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage{subfiles}
\usepackage{subfig}
\usepackage{amsmath}

@@

\begin{center}
\fontsize{14}{20}{\bf Accurate Measurement of Bicycle Parameters}
\end{center}

@@

@@

    \subfloat[]{\label{fig:triangle}\includegraphics[width=3in]{../../../figures/triangle.pdf}}

@@

		\includegraphics[width=3in]{../../../images/level.jpg}

@@

The period for a damped oscillation is
\begin{equation}
    T = \frac{2\pi}{\sqrt{1-\zeta^2}\omega_n}
    \label{eqn:periodDamped}
\end{equation}
and for light damping
\begin{equation}
    T \approx \frac{2\pi}{\omega_n}
    \label{eqn:period}
\end{equation}
The uncertainty in the period, $T$, can be determined from the fit. Firstly,
the variance of the fit is
\begin{equation}
    \sigma_y^2 =
    \frac{1}{N-5}\sum_{i=1}^N(y_{mi}-\bar{y}_m)^2-(y_{pi}-\bar{y}_m)^2
    \label{eqn:fitVariance}
\end{equation}
The covariance matrix of the fit function can be formed
\begin{equation}
    \mathbf{U} = \sigma_y^2\mathbf{H}^{-1}
    \label{eqn:covariance}
\end{equation}
where $\mathbf{H}$ is the Hessian~\cite{Hubbard1989b}. $\mathbf{U}$ is a $5\times5$ matrix with the
variances of each of the five fit parameters along the diagonal. This assumes
that the parameters are uncorrelated [note for Jason: you may have to take into
account correlation for this..maybe checkout the R function for nls]. The
variance of $T$ can be computed using the variance of $\zeta$ and $\omega$. It
is important to note that the uncertainties in the period are very low
($<10e-4$), even for the fits with low $r^2$ values due to the beating issue.
\subsection{Torsional Pendulum}
A torsional pendulum was used to measure all of moments of inertia about axes
in the lateral symmetric plane of each of the wheels, fork and frame. The
pendulum is made up of a rigid mount, an upper clamp, a torsion rod, and
various lower clamps.
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/fixture.jpg}
    \end{center}
    \caption{The rigid pendulumfixture mounted to a concrete column.}
    \label{fig:fixture}
\end{figure}
A 5mm diameter, 1m long mild steel rod was used as the torsion
spring. A lightweight, low relative moment of inertia clamp was constructed
that could clamp the rim and the tire. The wheel was hung freely such that the
center of mass aligned with the torsional pendulum axis and then it was
secured. The wheel was then perturbed and it oscillated about the pendulum axis.
The rate gyro was mounted on the clamp in line with the pendulum axis. The
radial moment of inertia can can calculated as such:
\begin{figure}[tbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/rod.jpg}
    \end{center}
    \caption{The steel calibration rod.}
    \label{fig:rod}
\end{figure}
The torsional pendulum was calibrated using a known moment of inertia.
A torsional pendulum almost identical to the one used in
\cite{Kooijman2006} was used to measure the averaged period $\overline{T}_i$ of
oscillation of the rear frame at three different
orientation angles $\beta_i$, where $i=1$, $2$, $3$, as shown in
Fig.~\ref{fig:triangle}. The parts were perturbed lightly, less than 1 degree,
and allowed to oscillate about the pendulum axis through at least ten periods.
The time of oscillation was recorded via a stopwatch ($\pm1$~s). This was done
three times for each frame and the recorded times were averaged. The
coefficient of elasticity $k$ for the torsional pendulum had previously been
measured in \cite{Kooijman2006} and found to be $k=5.01\pm0.01$
$\frac{\textrm{Nm}}{\textrm{rad}}$.

\subsection{Wheels}
The wheels are assumed to be symmetric laterally and about any radial axis. Thus only two
moment's of inertia are required. The moment of inertia about the axle was
measured by hanging the wheel as a compound pendulum. The wheel was hung on a
horizontal rod and perturbed to oscillate about the axis of the rod. This rate
gyro was attached to the spokes near the hub and orientated mostly along the
axle axis. The wheels tended to precess at the contact point about the vertical
axis. This adds a very low frequency component of rate along the vertical axis,
but should not affect the compound pendulum axis. A better fixture for the
wheel could prevent the precession. The pendulum arm length is the distance
from the rod/rim contact point to the mass center of the wheel. The inner
diameter of the rim was measured and divided by two to get $l$. The moment of
inertia about the axle is calculated by:
\begin{equation}
    I_{\mathrm{R}yy} = \left(\frac{\bar{T}}{2\pi}\right)^2m_\mathrm{R}gl_\mathrm{R} -
    m_\mathrm{R}l^2
\end{equation}
\begin{figure}[tbp]
    \centering
    \subfloat[]{
        \label{fig:FwheelTor}
        \includegraphics[width=3in]{../../../images/CrescendoFwheelTorsionalFirst.jpg}
    }
    \quad
    \subfloat[]{
        \label{fig:wheelIyy}
        \includegraphics[width=3in]{../../../images/wheelIyy.jpg}
    }
    \caption{\subref{fig:FwheelTor} The front wheel of the Crescendo hung as a
    torsional pendulum. \subref{fig:wheelIyy} A wheel hung as a compound pendulum.}
    \label{fig:wheelPend}
\end{figure}
The radial moment of inertia was measured by hanging the wheel as a torsional
pendulum. A 5mm diameter, 1m long mild steel rod was used as the torsion
spring. A lightweight, low relative moment of inertia clamp was constructed
that could clamp the rim and the tire. The wheel was hung freely such that the
center of mass aligned with the torsional pendulum axis and then it was
secured. The wheel was then perturbed and it oscillated about the pendulum axis.
The rate gyro was mounted on the clamp in line with the pendulum axis. The
radial moment of inertia can can calculated as such:
\begin{equation}
    I_{xx} = \frac{k\bar{T}^2}{4\pi^2}
\end{equation}
Finding the inertia tensors of the wheels is less complex because the wheels
are symmetric about three orthogonal planes so there are no products of
inertia. The $I_{xx}=I_{zz}$ moments of inertia were calculated by measuring
the averaged period of oscillation about an axis in the $XZ$-plane using the
torsional pendulum setup and Eq.~\ref{eq:torPend}. The $I_{yy}$ moment of
inertia was calculated with a compound pendulum as described in
\cite{Kooijman2006} and shown in Fig. using
\begin{equation}
	I_{yy}=\left(\frac{\overline{T}}{2\pi}\right)^2mgl-ml^2
\label{eq:comPend}
\end{equation}
where $l=0.303\pm0.002$ m is the pendulum length, $m$ is the mass of the wheel,
$\overline{T}$ is the averaged period and $g$ is the local acceleration due to
gravity. Table  gives the calculated values.
\subsection{Frame}
Three measurements were made to estimate the globally referenced moments and
products of inertia ($I_{xx}$, $I_{xz}$ and $I_{zz}$) of the rear frame. The
frame was typically hung from the three main tubes: seat tube, down tube
and top tube. The rear fender prevented easy connection to the seat tube on
some of the bikes and the clamp was attached to the fender. The fender was
generally less rigid than the frame tube. For best accuracy with only three orientation angles, the frame
should be hung at three angles that are $120^\circ$ apart. The three tubes on
the frame generally provide that the orientation angles were spread evenly at
about $120^\circ$. Taking data at more orientation angles could improve the accuracy further and
is gernally possible with standard diamond frame bicylces.

@@

The moments and products of inertia of the rear frame and handlebar/fork
assembly with reference to the benchmark coordinate system were calculated by
formulating the relationship between inertial frames
\begin{equation}
	\mathbf{J}_i=\mathbf{R}_i^T\mathbf{IR}_i
\label{eq:rotIn}
\end{equation}
where $\mathbf{J}_i$ is the inertia tensor about the pendulum axes,
$\mathbf{I}$, is the inertia tensor in the global reference frame and
$\mathbf{R}$ is the rotation matrix relating the two frames. The global inertia
tensor is defined as
\begin{equation}
	\mathbf{I}=
	\left[
	\begin{array}{rr}
		I_{xx}  & -I_{xz}\\
		-I_{xz} & I_{zz}
	\end{array}
	\right]\textrm{.}
	\label{eq:MoI}
\end{equation}
The inertia tensor can be reduced to a $2\times2$ matrix because the frame is
assumed to be laterally symmetric and the $y$ axis of the pendulum reference is
the same as the $y$ axis of the benchmark reference frame. The simple rotation matrix about the $Y$-axis
can similarly be reduced to a $2\times2$ matrix where $s_{\beta i}$ and
$c_{\beta i}$ are defined as $\sin{\beta_i}$ and $\cos{\beta_i}$,
respectively.
\begin{equation}
	\mathbf{R}=
	\left[
	\begin{array}{rr}
		c_{\beta i} & s_{\beta i}\\
		-s_{\beta i} & c_{\beta i}
	\end{array}
	\right]
	\label{eq:rotMat}
\end{equation}
The first entry of $\mathbf{J}_i$ in Eq.~\ref{eq:rotIn} is the moment of inertia about the pendulum axis and is written explicitly as 
\begin{equation}
	J_{i}=c^{2}_{\beta i}I_{xx}+2s_{\beta i}c_{\beta i}I_{xz}+s^{2}_{\beta i}I_{zz}\textrm{.}
\label{eq:inRelComp}
\end{equation}
Calculating all three $J_{i}$ allows one to form
\begin{equation}
	\left[
	\begin{array}{c}
		J_{1}\\
		J_{2}\\
		J_{3}
	\end{array}
	\right]
	=
	\left[
	\begin{array}{ccc}
		c_{\beta 1}^2 & -2s_{\beta 1}c_{\beta 1} & s_{\beta 1}^2\\
		c_{\beta 2}^2 & -2s_{\beta 2}c_{\beta 2} & s_{\beta 2}^2\\
		c_{\beta 3}^2 & -2s_{\beta 3}c_{\beta 3} & s_{\beta 3}^2
	\end{array}
	\right]
	\left[
	\begin{array}{c}
		I_{xx}\\
		I_{xz}\\
		I_{zz}
	\end{array}
	\right]
\label{eq:inRel}
\end{equation}
and the unknown global inertia tensor can be solved for.
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/YellowFrameCompoundFirst.jpg}
    \end{center}
    \caption{The rear frame hung as a compound pendulum.}
    \label{fig:FrameCompound}
\end{figure}

\subsection{Fork}
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/StratosForkTorsionalThird.jpg}
    \end{center}
    \caption{The Stratos fork and handlebar assembly hung as a torsional
    pendulum.}
    \label{fig:StratosFork}
\end{figure}
\section{Parameters}
\section{Linear Analysis}
\subsection{Canonical Matrices}
The final results are presented in the form used by the benchmark model. These
can be used to populate the canonical form
of the linear benchmark equations of motion presented in
\cite{Meijaard2007}.
\subsection{Eigenvalues}
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../plots/Bike/CrescendoRootLoci.png}
    \end{center}
    \caption{The root loci with speed as the parameter for the Crescendo.}
    \label{fig:rootloci}
\end{figure}

\subsection{Frequency Response}
\bibliographystyle{acm}
\bibliography{bicycle}
\end{document}

>>>>

%\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage{subfiles}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{pdflscape}

@@

% title
\begin{center}
\fontsize{14}{20}{\bf Accurate Measurement of Bicycle Parameters}
\end{center}

@@

\section{PARAMETERS}
The 25 parameters can be estimated by many techniques. Where possible we
measured the benchmark parameter directly.

@@

    \subfloat[]{\label{fig:triangle}\includegraphics[width=2.75in]{../../../figures/triangle.pdf}}

@@

		\includegraphics[width=3in]{../../../images/YellowFrameTorsionalThird.jpg}

@@

The period for a damped oscillation is
\begin{equation}
    T = \frac{2\pi}{\sqrt{1-\zeta^2}\omega_n}
    \label{eqn:periodDamped}
\end{equation}
and for light damping
\begin{equation}
    T \approx \frac{2\pi}{\omega_n}
    \label{eqn:period}
\end{equation}
The uncertainty in the period, $T$, can be determined from the fit. Firstly,
the variance of the fit is
\begin{equation}
    \sigma_y^2 =
    \frac{1}{N-5}\sum_{i=1}^N(y_{mi}-\bar{y}_m)^2-(y_{pi}-\bar{y}_m)^2
    \label{eqn:fitVariance}
\end{equation}
The covariance matrix of the fit function can be formed
\begin{equation}
    \mathbf{U} = \sigma_y^2\mathbf{H}^{-1}
    \label{eqn:covariance}
\end{equation}
where $\mathbf{H}$ is the Hessian~\cite{Hubbard1989b}. $\mathbf{U}$ is a $5\times5$ matrix with the
variances of each of the five fit parameters along the diagonal. This assumes
that the parameters are uncorrelated [note for Jason: you may have to take into
account correlation for this..maybe checkout the R function for nls]. The
variance of $T$ can be computed using the variance of $\zeta$ and $\omega$. It
is important to note that the uncertainties in the period are very low
($<10e-4$), even for the fits with low $r^2$ values due to the beating issue.
\subsection{Torsional Pendulum}
A torsional pendulum was used to measure all of moments of inertia about axes
in the lateral symmetric plane of each of the wheels, fork and frame. The
pendulum is made up of a rigid mount, an upper clamp, a torsion rod, and
various lower clamps.
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=3in]{../../../images/fixture.jpg}
    \end{center}
    \caption{The rigid pendulumfixture mounted to a concrete column.}
    \label{fig:fixture}
\end{figure}
A 5mm diameter, 1m long mild steel rod was used as the torsion
spring. A lightweight, low relative moment of inertia clamp was constructed
that could clamp the rim and the tire. The wheel was hung freely such that the
center of mass aligned with the torsional pendulum axis and then it was
secured. The wheel was then perturbed and it oscillated about the pendulum axis.
The rate gyro was mounted on the clamp in line with the pendulum axis. The
radial moment of inertia can can calculated as such:
\begin{figure}[tbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/rod.jpg}
    \end{center}
    \caption{The steel calibration rod.}
    \label{fig:rod}
\end{figure}
The torsional pendulum was calibrated using a known moment of inertia.
A torsional pendulum almost identical to the one used in
\cite{Kooijman2006} was used to measure the averaged period $\overline{T}_i$ of
oscillation of the rear frame at three different
orientation angles $\beta_i$, where $i=1$, $2$, $3$, as shown in
Fig.~\ref{fig:triangle}. The parts were perturbed lightly, less than 1 degree,
and allowed to oscillate about the pendulum axis through at least ten periods.
The time of oscillation was recorded via a stopwatch ($\pm1$~s). This was done
three times for each frame and the recorded times were averaged. The
coefficient of elasticity $k$ for the torsional pendulum had previously been
measured in \cite{Kooijman2006} and found to be $k=5.01\pm0.01$
$\frac{\textrm{Nm}}{\textrm{rad}}$.

\subsection{Wheels}
The wheels are assumed to be symmetric laterally and about any radial axis. Thus only two
moment's of inertia are required. The moment of inertia about the axle was
measured by hanging the wheel as a compound pendulum. The wheel was hung on a
horizontal rod and perturbed to oscillate about the axis of the rod. This rate
gyro was attached to the spokes near the hub and orientated mostly along the
axle axis. The wheels tended to precess at the contact point about the vertical
axis. This adds a very low frequency component of rate along the vertical axis,
but should not affect the compound pendulum axis. A better fixture for the
wheel could prevent the precession. The pendulum arm length is the distance
from the rod/rim contact point to the mass center of the wheel. The inner
diameter of the rim was measured and divided by two to get $l$. The moment of
inertia about the axle is calculated by:
\begin{equation}
    I_{\mathrm{R}yy} = \left(\frac{\bar{T}}{2\pi}\right)^2m_\mathrm{R}gl_\mathrm{R} -
    m_\mathrm{R}l^2
\end{equation}
\begin{figure}[tbp]
    \centering
    \subfloat[]{
        \label{fig:FwheelTor}
        \includegraphics[width=2.75in]{../../../images/CrescendoFwheelTorsionalFirst.jpg}
    }
    \quad
    \subfloat[]{
        \label{fig:wheelIyy}
        \includegraphics[width=2.75in]{../../../images/wheelIyy.jpg}
    }
    \caption{\subref{fig:FwheelTor} The front wheel of the Crescendo hung as a
    torsional pendulum. \subref{fig:wheelIyy} A wheel hung as a compound pendulum.}
    \label{fig:wheelPend}
\end{figure}
The radial moment of inertia was measured by hanging the wheel as a torsional
pendulum. A 5mm diameter, 1m long mild steel rod was used as the torsion
spring. A lightweight, low relative moment of inertia clamp was constructed
that could clamp the rim and the tire. The wheel was hung freely such that the
center of mass aligned with the torsional pendulum axis and then it was
secured. The wheel was then perturbed and it oscillated about the pendulum axis.
The rate gyro was mounted on the clamp in line with the pendulum axis. The
radial moment of inertia can can calculated as such:
\begin{equation}
    I_{xx} = \frac{k\bar{T}^2}{4\pi^2}
\end{equation}
Finding the inertia tensors of the wheels is less complex because the wheels
are symmetric about three orthogonal planes so there are no products of
inertia. The $I_{xx}=I_{zz}$ moments of inertia were calculated by measuring
the averaged period of oscillation about an axis in the $XZ$-plane using the
torsional pendulum setup and Eq.~\ref{eq:torPend}. The $I_{yy}$ moment of
inertia was calculated with a compound pendulum as described in
\cite{Kooijman2006} and shown in Fig. using
\begin{equation}
	I_{yy}=\left(\frac{\overline{T}}{2\pi}\right)^2mgl-ml^2
\label{eq:comPend}
\end{equation}
where $l=0.303\pm0.002$ m is the pendulum length, $m$ is the mass of the wheel,
$\overline{T}$ is the averaged period and $g$ is the local acceleration due to
gravity. Table  gives the calculated values.
\subsection{Frame}
Three measurements were made to estimate the globally referenced moments and
products of inertia ($I_{xx}$, $I_{xz}$ and $I_{zz}$) of the rear frame. The
frame was typically hung from the three main tubes: seat tube, down tube
and top tube. The rear fender prevented easy connection to the seat tube on
some of the bikes and the clamp was attached to the fender. The fender was
generally less rigid than the frame tube. For best accuracy with only three orientation angles, the frame
should be hung at three angles that are $120^\circ$ apart. The three tubes on
the frame generally provide that the orientation angles were spread evenly at
about $120^\circ$. Taking data at more orientation angles could improve the accuracy further and
is gernally possible with standard diamond frame bicylces.

@@

The moments and products of inertia of the rear frame and handlebar/fork
assembly with reference to the benchmark coordinate system were calculated by
formulating the relationship between inertial frames
\begin{equation}
	\mathbf{J}_i=\mathbf{R}_i^T\mathbf{IR}_i
\label{eq:rotIn}
\end{equation}
where $\mathbf{J}_i$ is the inertia tensor about the pendulum axes,
$\mathbf{I}$, is the inertia tensor in the global reference frame and
$\mathbf{R}$ is the rotation matrix relating the two frames. The global inertia
tensor is defined as
\begin{equation}
	\mathbf{I}=
	\left[
	\begin{array}{rr}
		I_{xx}  & -I_{xz}\\
		-I_{xz} & I_{zz}
	\end{array}
	\right]\textrm{.}
	\label{eq:MoI}
\end{equation}
The inertia tensor can be reduced to a $2\times2$ matrix because the frame is
assumed to be laterally symmetric and the $y$ axis of the pendulum reference is
the same as the $y$ axis of the benchmark reference frame. The simple rotation matrix about the $Y$-axis
can similarly be reduced to a $2\times2$ matrix where $s_{\beta i}$ and
$c_{\beta i}$ are defined as $\sin{\beta_i}$ and $\cos{\beta_i}$,
respectively.
\begin{equation}
	\mathbf{R}=
	\left[
	\begin{array}{rr}
		c_{\beta i} & s_{\beta i}\\
		-s_{\beta i} & c_{\beta i}
	\end{array}
	\right]
	\label{eq:rotMat}
\end{equation}
The first entry of $\mathbf{J}_i$ in Eq.~\ref{eq:rotIn} is the moment of inertia about the pendulum axis and is written explicitly as 
\begin{equation}
	J_{i}=c^{2}_{\beta i}I_{xx}+2s_{\beta i}c_{\beta i}I_{xz}+s^{2}_{\beta i}I_{zz}\textrm{.}
\label{eq:inRelComp}
\end{equation}
Calculating all three $J_{i}$ allows one to form
\begin{equation}
	\left[
	\begin{array}{c}
		J_{1}\\
		J_{2}\\
		J_{3}
	\end{array}
	\right]
	=
	\left[
	\begin{array}{ccc}
		c_{\beta 1}^2 & -2s_{\beta 1}c_{\beta 1} & s_{\beta 1}^2\\
		c_{\beta 2}^2 & -2s_{\beta 2}c_{\beta 2} & s_{\beta 2}^2\\
		c_{\beta 3}^2 & -2s_{\beta 3}c_{\beta 3} & s_{\beta 3}^2
	\end{array}
	\right]
	\left[
	\begin{array}{c}
		I_{xx}\\
		I_{xz}\\
		I_{zz}
	\end{array}
	\right]
\label{eq:inRel}
\end{equation}
and the unknown global inertia tensor can be solved for.
\begin{figure}[tbp]
    \centering
    \subfloat[]{
        \label{fig:frameCompound}
        \includegraphics[width=2.75in]{../../../images/YellowFrameCompoundFirst.jpg}
        }
    \subfloat[]{
        \label{fig:forkCompound}
        \includegraphics[width=2.75in]{../../../images/BrowserInsForkCompoundFirst.jpg}
        }
        \caption{\subref{fig:frameCompound} The rear frame hung as a compound
        pendulum. \subref{fig:forkCompound} The Browser fork hung as a
        compound pendulum.}
        \label{fig:compound}
\end{figure}
\subsection{Fork}
\begin{figure}[tbp]
    \centering
    \subfloat[]{
        \label{fig:StratosFork}
        \includegraphics[width=2.75in]{../../../images/StratosForkTorsionalThird.jpg}
        }
    \caption{\subref{fig:StratosFork} The Stratos fork and handlebar assembly hung as a torsional
        pendulum.}
    \label{fig:torsional}
\end{figure}
\section{LINEAR ANALYSIS}
Once all of the bicycle parameters have been calculated the canonical matrices
can be formed and the linear dynamics of the bicycles can be explored. We also
added the same rigid rider to each bicycle for further comparison.
\begin{table}[tbp]
    \centering
    \caption{Rider parameters}
    \begin{tabular}{ll}
        Parameter & Value\\
        \hline
        $m_\mathrm{P}$ [kg] & 72\\
        $x_\mathrm{P}$ [m] & 0.2909\\
        $z_\mathrm{P}$ [m] & -1.1091\\
        $I_\mathrm{P}$ [$\mathrm{kg\ m}^2$] &
            $\left[
            \begin{array}{ccc}
                 7.9985 & 0      & -1.9272\\
                 0      & 8.0689 & 0\\
                -1.9272 & 0      & 2.3624
            \end{array}
            \right]$
    \end{tabular}
\end{table}

\subsection{EIGENVALUES}
\begin{figure}[tbp]
    \centering
    \includegraphics[width=4in]{../../../plots/Bike/eig_plot.pdf}
    \caption{The eigenvalues verus speed for all eight bicycles.}
    \label{fig:bikeEigPlot}
\end{figure}
\begin{figure}[tbp]
    \begin{center}
        \includegraphics[width=4in]{../../../plots/Bike/CrescendoRootLoci.pdf}
    \end{center}
    \caption{The root loci with speed as the parameter for the Crescendo.}
    \label{fig:rootloci}
\end{figure}
\begin{figure}[tbp]
    \centering
    \includegraphics[width=4in]{../../../plots/BikeRider/eig_plot.pdf}
    \caption{The eigenvalues verus speed for all eight bicycles with the same
    rider.}
    \label{fig:bikeRiderEigPlot}
\end{figure}
\subsection{FREQUENCY RESPONSE}
\bibliographystyle{acm}
\bibliography{bicycle}
\appendix
\section{PARAMETERS}
\subsection{BICYCLE}
\begin{landscape}
\subfile{../../../tables/Bike/Parameters/MasterParTable.tex}
\end{landscape}
\subsection{BICYCLE WITH RIDER}
%\begin{landscape}
%\subfile{../../../tables/Bike/Parameters/MasterParTable.tex}
%\end{landscape}
\section{CANONICAL MATRICES}
\subsection{BICYCLE}
\begin{landscape}
\subfile{../../../tables/Bike/Canonical/MasterCanTable.tex}
\end{landscape}
\subsection{BICYCLE WITH RIDER}
%\begin{landscape}
%\subfile{../../../tables/Bike/Parameters/MasterParTable.tex}
%\end{landscape}
\end{document}
